The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-07-02 head.tex
首先 要区分框架，包括总体和具体运行框架。抓住一个点。明确系统的输入和输出，控制的目标函数之类的。

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In Cloud Manufacturing, user do manufacturing business with well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product. This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.

>>>>

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In Cloud Manufacturing, users engage in manufacturing business through the well-designed platform framework, where provider publish manufacturing resource as service for demander to search and purchase it as product. This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
